Tulai

### 2023-11-06 paper/paper.qmd
update chi-sq figs

worldplot <- 
ggplot(data = world) +
     geom_sf(color = "black", 
             fill = "white",
             linewidth = 0.05) +
    annotate("rect",
           xmin = bbox[3],
           xmax = bbox[1],
           ymin = bbox[2],
           ymax = bbox[4],
           fill = NA,
           colour = "red",
           size = 1.5
  ) +
  theme_void() +
  theme(panel.background = element_rect(fill = "white"))

@@

@@

@@

>>>>

worldplot <- 
ggplot(data = world) +
     geom_sf(color = "black", 
             fill = "white",
             linewidth = 0.05) +
    annotate("rect",
           xmin = bbox[3],
           xmax = bbox[1],
           ymin = bbox[2],
           ymax = bbox[4],
           fill = NA,
           colour = "red",
           linewidth = 1.5
  ) +
  theme_void() +
  theme(panel.background = element_rect(fill = "white"))

@@

ggsave(here::here("figures/fig-chi-sq-residuals-tool-type-freqs1.jpg"),
       h = 4, 
       w = 4)

@@

BM: I don't understand what is the difference between the two chi-square tests where have here (above and below). Can you please clarify?

@@

ggsave(here::here("figures/fig-chi-sq-residuals-tool-type-freqs2.jpg"),
       h = 4, 
       w = 4)
